### 2019-08-26 concepts.tex
work on some issues

Delta-debugging \cite{DD}\footnote{We use delta-debugging to stand for
  all test reduction algorithms, even those \cite{CReduce,tstl} that do not use the exact
  binary-search that distinguishes delta-debugging \emph{per se}; the
  differences are immaterial for our purposes.}  is a widely used method for reducing the
size of failing tests, making them easier to understand and debug.
The core idea of delta-debugging is to take a test that satisfies some
property (usually the property is ``it fails in a particular way'')
and produce a smaller test that satisfies the same property.
Delta-debugging, as proposed by Zeller and Hildebrandt, relies on a
modified binary search to produce this smaller test, though the
following discussion relies only on the general structure of
delta-debugging, and also applies to the greedy algorithms used to
reduce failing tests in some work \cite{CReduce,onetest}.

>>>>

Delta-debugging \cite{DD}\footnote{We use delta-debugging to stand for
  all test reduction algorithms, even those \cite{CReduce,tstl} that do not use the exact
  binary-search that distinguishes delta-debugging \emph{per se}; the
  differences are immaterial for our purposes.}  is a widely used method for reducing the
size of failing tests, making them easier to understand and debug.
The core idea of delta-debugging is to take a test that satisfies some
property (usually the property is ``it fails in a particular way'')
and produce a smaller test that satisfies the same property.
Delta-debugging, as proposed by Zeller and Hildebrandt, relies on a
modified binary search to produce this smaller test, though the
following discussion relies only on the general structure of
delta-debugging, and also applies to the greedy algorithms used to
reduce failing tests in some work \cite{CReduce,onetest}.  At a high
level delta-debugging and other test reduction/shrinking algorithms
can be seen as following a general algorithmic structure.  Given a
test case, $T_{\mathit{INIT}} : \mathit{test}$ and a predicate $\mathit{PRED}: \mathit{test} \rightarrow \mathit{bool}$

\begin{enumerate}
\item $T_{\mathit{CURR}} = T_{\mathit{INIT}}$
\item Let $T_{\mathit{NEXT}} =$ a variation of $T_{\mathit{CURR}}$
  that has not yet been tried.  If there are no further variations of
  $T_{\mathit{CURR}}$, stop and return $T_{\mathit{CURR}}$ as the
  reduced test.
\item Add $T_{\mathit{NEXT}}$ to the set of variations that have been
  tried.
\item If $\mathit{PRED}(T_{\mathit{NEXT}})$, set $T_{\mathit{CURR}} =
  T_{\mathit{NEXT}}$.
\item Go to 2.
\end{enumerate}

The behavior of a particular algorithm for reducing a test can usually
be specified simply be elaborating the construction and ordering of
the variations considered.  For our purposes, the essential point is
to note that any such algorithm will apply $\mathit{PRED}$ to a
potentially very large number of tests.
